Draft_Application_Stochastic_Volatility

### 2021-08-10 Real Dataset SV.Rmd
commit

```{r include=FALSE}
Errorcomp1<-matrix(NA,ncol=6,nrow=10)
colnames(Errorcomp1)<-c("N","BPF", "GPFOPT", "APF", "BAPF","SIS")
rownames(Errorcomp1)<-c("RMSE","RMSE","RMSE","RMSE","RMSE","MAE","MAE","MAE","MAE","MAE")
Errorcomp1[,1]<-c(10,100,1000,5000,10000,10,100,1000,5000,10000)
Errorcomp1[,2]<-c(0.4233094,0.15689352,0.06901099,0.03817009,0.03045272,0.2807802,0.09658088,0.03312132,0.01889245,0.01455814)
Errorcomp1[,3]<-c(0.3685259,0.15094281,0.07669050,0.03568058,0.02709059,0.2796141,0.09623692,0.03696833,0.01664805,0.01422964)
Errorcomp1[,4]<-c(0.5478362,0.2404408,0.08878446,0.05742351,0.04295610,0.4310335,0.1756985,0.05538968,0.03186140,0.02448565)
Errorcomp1[,5]<-c(0.5595929,0.2348842,0.10295053,0.06109947,0.05151115,0.4377886,0.1839363,0.06726034,0.03448388,0.02726281)
Errorcomp1[,6]<-c(0.9168639,1.1055065,0.6250516,0.6200359,0.5118927,0.7275327,0.9179852,0.4971839,0.4475265,0.406363)

@@

```{r include=FALSE}
Errorcomp2<-matrix(NA,ncol=6,nrow=10)
colnames(Errorcomp2)<-c("N","BPF", "GPFOPT", "APF", "BAPF", "SIS")
rownames(Errorcomp2)<-c("RMSE","RMSE","RMSE","RMSE","RMSE","MAE","MAE","MAE","MAE","MAE")
Errorcomp2[,1]<-c(10,100,1000,5000,10000,10,100,1000,5000,10000)
Errorcomp2[,2]<-c(0.4054868,0.13510456,0.04145471,0.02847469,0.03048093,0.2726597,0.08539766,0.02328878,0.01755582,0.01417144)
Errorcomp2[,3]<-c(0.3495018,0.14208597,0.06873795,0.04921716,0.03336987,0.2694089,0.09033775,0.03531985,0.02409677,0.01717600)
Errorcomp2[,4]<-c(0.5323702,0.2224267,0.07796291,0.03931358,0.02647522,0.4215135,0.1669123,0.05105029,0.02662432,0.01973858)
Errorcomp2[,5]<-c(0.5459719,0.2239766,0.07692431,0.05229897,0.02410626,0.4290946,0.1748428,0.05753199,0.03275473,0.01741627)
Errorcomp2[,6]<-c(0.9103835,1.101557,0.6150409,0.6117618,0.5054665,0.7211173,0.914675,0.4895908,0.4419522,0.4022079)

@@

#Auxiliary Particle Filter (PETRONE p 218)
#-------------------------
SVAPFfun_2<-function(data,N,m0,C0,alpha,beta,tau,r){
  if(missing(r)){r=2}else{}
  xs<-NULL
  ws<-NULL
  ess<-NULL
  x  = rnorm(N,m0,sqrt(C0))
  w  = rep(1/N,N)

  for(t in 1:length(data)){
    x_prev=x
    x_hat = alpha+beta*x #means of the transition from the previous particle 
    I_k = sample(1:N,prob=w*dnorm(data[t],0,sqrt(exp((x_hat)/2))))
    for(k in 1:N){
      x[k]=rnorm(size=1,mean=alpha+beta*x_prev[I_k],sd=tau)
      w[k]=dnorm(data[t],0,sqrt(exp((x[k])/2)))/dnorm(data[t],0,sqrt(exp((x_hat)/2)))
    }
    w = w/sum(w)
    ESS  = 1/sum(w^2)

    xs = rbind(xs,x)
    ws = rbind(ws,w)
    ess =rbind(ess,ESS)

>>>>

```{r include=FALSE}
Errorcomp1<-matrix(NA,ncol=6,nrow=10)
colnames(Errorcomp1)<-c("N","BPF", "GPFOPT", "APF", "BAPF","SIS")
rownames(Errorcomp1)<-c("RMSE","RMSE","RMSE","RMSE","RMSE","MAE","MAE","MAE","MAE","MAE")
Errorcomp1[,1]<-c(10,100,1000,5000,10000,10,100,1000,5000,10000)
Errorcomp1[,2]<-c(0.3017986,0.11645976,0.02906876,0.01511962,0.010462488,0.2342816,0.08340162,0.02145381,0.01110398,0.008013466)
Errorcomp1[,3]<-c(0.3367199,0.09173166,0.03356642,0.01461339,0.009572002,0.2539500,0.06764348,0.02447722,0.01026689,0.007198043)
Errorcomp1[,4]<-c(0.4822315,0.1647978,0.05644653,0.02657352,0.02006171,0.3648792,0.1159503,0.03722911,0.01879724,0.01420517)
Errorcomp1[,5]<-c(0.4561433,0.1740267,0.04786161,0.02741662,0.02085289,0.3643665,0.1352035,0.03833600,0.01939683,0.01481767)
Errorcomp1[,6]<-c(1.566291,1.770554,1.1788696,0.9680993,0.9301619,1.256867,1.396812,0.8683638,0.7212099,0.7182857)

@@

```{r include=FALSE}
Errorcomp2<-matrix(NA,ncol=6,nrow=10)
colnames(Errorcomp2)<-c("N","BPF", "GPFOPT", "APF", "BAPF", "SIS")
rownames(Errorcomp2)<-c("RMSE","RMSE","RMSE","RMSE","RMSE","MAE","MAE","MAE","MAE","MAE")
Errorcomp2[,1]<-c(10,100,1000,5000,10000,10,100,1000,5000,10000)
Errorcomp2[,2]<-c(0.2998373,0.11719984,0.03339627,0.02213888,0.01879835,0.2334205,0.08306614,0.02414570,0.01444042,0.01184698)
Errorcomp2[,3]<-c(0.3365006,0.09527023,0.03979288,0.02073930,0.01744916,0.2540961,0.06926543,0.02793461,0.01360319,0.01149824)
Errorcomp2[,4]<-c(0.4828496,0.1665464,0.05696147,0.03056349,0.01929485,0.3651631,0.1174350,0.03692383,0.02031451,0.01437991)
Errorcomp2[,5]<-c(0.4555563,0.1715253,0.04847040,0.02916413,0.02211777,0.3634416,0.1343189,0.03877838,0.02075878,0.01495394)
Errorcomp2[,6]<-c(1.565179,1.770452,1.1782202,0.9681921,0.9298538,1.254832,1.397196,0.8666459,0.7203661,0.7181958)

@@
